Contextual Combinatorial Cascading Bandits

### 2015-12-10 contextual combinatorial cascading bandits.tex
update statement of main theorem

\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
\STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
\STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
%\STATE {}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
	observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{align}
R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
\end{align}
\begin{align}
R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
\end{align}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}

@@

\wei{This lemma needs to be clarified, using Lemma 4.6.
Also, our regret bound is expected regret but with a high probability? Sound a 
bit strange.}
\shuai{Yes, our regret bound is expected regret with a high probability. The reason is that NIPS'11 gives such a result.}

Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. However, $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ is hard to estimate because $\bV_t$ only contains observed base arms. So we need the following lemma.

\begin{lemma}
\label{lem:DeltaEsimateWithP*}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
$$
\EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&\EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  
\begin{align*}
&\EE[R(t, \bA_t)|\cH_t] \\
=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
\end{align*}
The third inequality is because $p_{\bA_t} \geq p^*$ and the forth inequality is by Lemma \ref{lem:DeltaEstimate}.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. Then we have
\begin{align*}
&\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t]\\
=& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right]\\
=& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
\leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]
% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bB_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
\end{align*}
By Lemma \ref{lem:increasing},
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
and by Lemma \ref{lem:estimateTech},
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Then we can derive the result
\begin{align*}
&\EE_t[R_{\wedge}(t, \bA_t)] \\
\leq& \EE \left[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
\leq& \EE \left[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]
\end{align*}
\end{proof}

@@

For the disjunctive case,
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \\
&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
	\right ]  \\
&\leq \EE\left[\frac{1}{p^*} \left(\sqrt{\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)} \right)} \right]\\
&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}
The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}. The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}, and mean inequality. The third inequality is because of the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}. And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

Similarly, for the conjunctive case, 
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \\
&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)} \right)} \right]\\
&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}
\end{proof}

>>>>

\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
\STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$ } 
\STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
%\STATE {}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
	observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{align}
R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
\end{align}
\begin{align}
R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
\end{align}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}

@@

Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. 
However, it is hard to estimate an upper bound for
	$\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ 
	because $\bV_t$ only contains observed base arms. Thus we need the following lemma.

\begin{lemma}
\label{lem:DeltaEsimateWithP*}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. 
For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. 
Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
$$
\EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&\EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  
\begin{align}
&\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
\end{align}
The third inequality is because $p_{\bA_t} \geq p^*$ and the forth inequality is by Lemma \ref{lem:DeltaEstimate}.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. 
By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge}
	\le \frac{1}{4} f^*_{\wedge,t}  $, we have
	$p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$.
Then we have
\begin{align}
&\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
=& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
=& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
\leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bB_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
\end{align}
Next, we have
\begin{equation} \label{eq:andstarbt}
f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
\end{equation}
where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing},
	the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected
	with respect to $\bU_t$, and the last inequality is by
	Lemma~\ref{lem:prefixRelation}~(2).

Then by Lemma \ref{lem:estimateTech},
\begin{equation} \label{eq:btuttrue}
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
\end{equation}
Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
\begin{align}
R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
& \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
\end{align}
Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}
we can derive the result
\begin{align*}
&\EE_t[R_{\wedge}(t, \bA_t)] \\
\leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
\leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
\end{align*}
\end{proof}

@@

For the disjunctive case,
\begin{equation}
\begin{split}
&R(T) = \EE[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] ]\\
&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
	\right ]  \\
&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \\
& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right)\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}
The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}. The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}, and mean inequality. The third inequality is because of the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}. And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

Similarly, for the conjunctive case, 
\begin{equation}
\begin{split}
&R(T) = \EE[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] ]\\
&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \\
&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right)\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}
\end{proof}
